The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation

### 2024-06-07 Restud submission/OA_restud.tex
prepare for restud submission

\newgeometry{margin=1in}
\begin{center}
	\Large ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing \\[0.5em]
	%\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

@@

%\section{ Treatment Explanation Materials and Pictures}
\section{Additional materials} 
%\vspace{.2in}
\begin{figure}[!h]
     \caption{Behavior of borrowers who lost their pawn.}
    \begin{center}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \footnotesize{This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
        \label{proxy_naive}
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

@@

\newpage
\subsection{Intermediate Outcomes}

\begin{landscape}

@@

\begin{table}[!h]
\caption{Lender's Profit}
\label{lenders_profit}
\begin{center}
 \footnotesize{\input{./Tables/lenders_profit.tex}}
\end{center}
 \footnotesize{ The dependent variable in column (1) is the profit formula in equation (\ref{profit_function}). Columns (2)-(3) are back-of-the-envelope computations of the lender's profit.
 Standard errors are clustered at the branch-day level.}
%\textit{Do file: } \texttt{lenders\_profit.do}
\end{table}

@@

To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
The functions \texttt{causal\_forest()} and \texttt{instrumental\_forest()} implement special cases of the ``generalized random forest'' methods of \cite{atheygrf}.
In broad strokes, these functions combine a large number of regression trees that recursively partition the covariate space to estimate conditional average effects.
% Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.
\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}. When constructing our random forest estimates of heterogeneous treatment effects, we use observations for all borrowers who answered at least \emph{part} of the intake survey.
We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value. Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness. This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}

\begin{figure}[!h]
     \caption{Heterogeneous Treatment Effects.} 
     \label{heterogeneous_effects}    
    \begin{center}
     \begin{subfigure}{0.35\textwidth}
       \centering
      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
          \caption{ToT}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
       \centering
      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
          \caption{TuT}
    \end{subfigure} 
       \begin{subfigure}{.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
        \caption{ATE}
    \end{subfigure} 
    \end{center}
  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
\end{figure}

>>>>

\newgeometry{margin=1in}
\begin{center}
	\Large ONLINE APPENDIX: The forcing-choice design and paternalism in pawnshop borrowing \\[0.5em]
	%\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

@@

%\section{ Treatment Explanation Materials and Pictures}
\section{Additional materials} 
%\vspace{.2in}

\begin{figure}[!h]
     \caption{Behavior of borrowers who lost their pawn.}
    \begin{center}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \footnotesize{This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
        \label{proxy_naive}
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

@@

\begin{table}[!h]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize{
Translation of the baseline questionnaire. Highlighted questions were used in the wide forest.}
\end{table}

\begin{landscape}
\subsection{Intermediate Outcomes}

@@

\begin{table}[!h]
\caption{Lender's Profit}
\label{lenders_profit}
\begin{center}
 \footnotesize{\input{./Tables/lenders_profit.tex}}
\end{center}
 \footnotesize{ The dependent variable in column (1) is the profit formula in equation (\ref{profit_function}). For columns (2)-(3) we compute average profit for borrower in arm $j$ according to (\ref{profit_function}). We then extrapolate the flow of payments over several periods depending on their repeat pawning behavior. In column (2) the flow of profits is given by
 \[\sum_{T=0}^{\infty}\text{Profit}_j\times\Pr(\text{Pawn}_j)^T\]
 assuming independence of repeat pawning across periods. In column (3) the stream of profits is given by
 \[\text{Profit}_j + \text{Profit}_j\times \Pr(\text{Pawn}_j) +\text{Profit}_j\times\Pr(\text{Pawn}_j) \]
 assuming that once learning (and hence repeat pawning behavior) occurs the borrower keeps coming back (we only keep 2 further periods for the exercise).
 For columns(2)-(3) we clustered-bootstrapped the standard error. All Standard errors are clustered at the branch-day level.}
%\textit{Do file: } \texttt{lenders\_profit.do}
\end{table}

@@

To estimate the conditional average treatment effects shown in Figure \ref{heterogeneous_effects}, we use administrative and survey data, and the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
The functions \texttt{causal\_forest()} and \texttt{instrumental\_forest()} implement special cases of the ``generalized random forest'' methods of \cite{atheygrf}.
In broad strokes, these functions combine a large number of regression trees that recursively partition the covariate space to estimate conditional average effects.
% Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.
\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}. When constructing our random forest estimates of heterogeneous treatment effects, we use observations for all borrowers who answered at least \emph{part} of the intake survey.
We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value. Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness. This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}
